### 2013-09-05 Tex/chapters/results.tex
Fehlerabhängigkeit von tau klarer formuliert

    Note that while the error of \(\avg{O}\), \(\Delta \avg{O}\) is dependend on \(\tau\) \cite[p. 151]{Katzgraber2011}
    \(\Delta \overline{\avg{O}}\) is not directly, because it is averaged
    over different realizations of the random proximity graph, which are
    surely uncorrelated.

>>>>

    Note that the error of \(\avg{O}\), which is the standard error\footnote{for the arthmetic mean: standard deviation divided by \(\sqrt M\), where \(M\) is the number of samples}
    of different states on one instance of a proximity graph \(\Delta \avg{O}\),
    is dependend on \(\tau\) \cite[p. 151]{Katzgraber2011}.
    However \(\Delta \overline{\avg{O}}\), which is the the error of the
    observable averaged over different instances of the proximity graphs,
    is not dependend on \(\tau\), because different realizations of the
    random proximity graph are surely uncorrelated.
